### 2015-08-03 doc/manual/inputParameters.tex
Additions to user manual

\section{The {\ttfamily otherNumericalParameters}~namelist}

@@

\PETScParam{-ksp\_gmres\_restart {\normalfont \ttfamily$<$integer$>$}}
{After how many iterations will GMRES restart. Default is 2000. The convergence of GMRES slows every time a restart occurs, but restarts also free up memory.}

@@

>>>>

\section{The {\ttfamily otherNumericalParameters}~namelist}
\label{sec:otherNumericalParameters}

@@

\PETScParam{-ksp\_gmres\_restart {\normalfont \ttfamily$<$integer$>$}}
{After how many iterations will GMRES restart. Default is 2000. The convergence of GMRES slows every time a restart occurs, but restarts also free up memory.
The memory required by GMRES is typically quite small compared to the memory required for the $LU$ factorization.}

\PETScParam{-pc\_factor\_mat\_solver\_package {\normalfont \ttfamily$<$packagename$>$}}
{Which sparse direct solver package is used to $LU$-factorize the preconditioner matrix.
%Options are given by the items in quotation marks  
%{\href{http://www.mcs.anl.gov/petsc/petsc-current/docs/manualpages/Mat/MatSolverPackage.html#MatSolverPackage}{here.}}
This command-line flag overrides the related namelist parameter\\
\parlink{whichParallelSolverToFactorPreconditioner}.
See section \ref{sec:solvers} for further information about the available packages.
}

\section{\mumps~commands}
\label{sec:mumpsControlParameters}

The \mumps~solver package has many control parameters which are documented in the manual,
available \href{http://mumps-solver.org/}{here}.
In \sfincs, as in any \PETSc~application, these control parameters can be set
using the command-line flags {\ttfamily -mat\_mumps\_cntl\_X YYYY} (for floating point parameters)
and {\ttfamily -mat\_mumps\_icntl\_X YYYY} (for integer control parameters). 
Here, {\ttfamily X} is the numeric index of the control parameter,
and {\ttfamily YYYY} is the desired setting.
Here we list some of the more useful options.\\

@@

\PETScParam{-mat\_mumps\_icntl\_14 {\normalfont \ttfamily$<$integer$>$}}
{Percentage margin allowed for increase of certain arrays during the $LU$ factorization.
The default value set by \sfincs~is 50 (higher than the original default value in \mumps.)
If \sfincs~exits with the \mumps~error {\ttfamily INFO(1)=-9}, then further increasing this parameter may help.}

\PETScParam{-mat\_mumps\_icntl\_22 1}
{Turns on the out-of-core solve capability,
which reduces the memory required at the cost of speed.
See section \ref{sec:parallelization} for further details.}

### 2015-08-03 doc/manual/resolution.tex
Additions to user manual

\section{Typical resolution requirements}

>>>>

\section{Examples of resolution requirements}

To estimate the appropriate resolution parameters for various circumstances, you can look at
the examples in the \path{sfincs/fortran/version3/examples/} directory. 
Some other examples of appropriate resolution parameters are given in the following sections.

\subsection{W7-X with anticipated experimental density and temperature}
\label{sec:w7xresolution}

The following parameters have been extensively tested with W7-X geometry for densities near $10^{20}$ m$^{-3}$
and temperatures up to 6 keV, and found to give convergence to $\sim 3$\% (as shown in figure \ref{fig:convergence2}):\\
{\ttfamily
\Ntheta = 19 \\
\Nzeta = 125 \\
\Nxi = 140 \\
\Nx = 5 \\
}
Note that at lower temperature and/or higher density, the collisionality will be higher,
so comparable convergence could be achieved at lower \parlink{Nzeta} and \parlink{Nxi}.
Conversely, at higher temperatures and/or lower desntiy, the collisionality will be lower,
so comparable convergence would likely require higher  \parlink{Nzeta} and \parlink{Nxi}.

\subsection{Figure 3 of the original SFINCS paper}

For figure 3 in Ref \cite{sfincsPaper}, corresponding to a pure plasma in W7-X with $n = 6.6\times 10^{19}$ m$^3$ and $T_i = T_e = 1$ keV,
the calculations used\\
{\ttfamily
\Ntheta = 19 \\
\Nzeta = 59 \\
\Nxi = 60 \\
\Nx = 5. \\
}
Note the lower values of  \parlink{Nzeta} and \parlink{Nxi} used compared to section \ref{sec:w7xresolution},
which were sufficient since the temperatures were lower.

\subsection{Figure 4 of the original SFINCS paper}

For figure 4 in Ref \cite{sfincsPaper}, corresponding to a collisionality scan in LHD,
the following resolution parameters were used:

\centerline{
\begin{tabular}{c|c|c|c|c}
\parlink{nuPrime} & \Ntheta & \Nzeta & \Nxi & \Nx \\
\hline
0.001 & 85 & 41 & 103 & 5 \\
0.01 & 21 & 25 & 70 & 5 \\
0.1 & 15 & 13 & 37 & 5 \\
0.3 & 15 & 13 & 34 & 6 \\
1 & 13 & 13 & 13 & 8 \\
10 & 15 & 13 & 13 & 8 \\
100 & 15 & 13 & 13 & 8
\end{tabular}
}

\subsection{Figure 5 of the original SFINCS paper}

For figure 5 in Ref \cite{sfincsPaper}, corresponding to a collisionality scan in W7-X,
the following resolution parameters were used:

\centerline{
\begin{tabular}{c|c|c|c|c}
\parlink{nuPrime} & \Ntheta & \Nzeta & \Nxi & \Nx \\
\hline
0.001 & 29 & 83 & 180 & 5 \\
0.01  & 11 & 64 & 100 & 5 \\
0.1   & 11 & 37 & 37  & 5 \\
0.3   & 11 & 29 & 30  & 5 \\
1     & 13 & 31 & 24  & 6 \\
10    & 13 & 35 & 12  & 7 \\
100   & 11 & 37 & 13  & 8
\end{tabular}
}
